The Minimal Retroreflective Microfacet Model

### 2025-10-30 article.tex

Rendering of retro-reflective materials is useful in a variety of contexts. For security garnments and signs, retroreflective appearances are heavily used. \todo{Different usage and forms} We known for measurements that retro-reflective tapes exhibit an imperfect (rough) retro-reflective lobe~\cite{BelcourBackvector}.

>>>>

Rendering of retro-reflective materials is useful in a variety of contexts. For security garments and signs, retroreflective appearances are heavily used. A number of CG models have been proposed. For practical purposes in visual effects, we are interested in a model which is a) visually plausible at least, b) provably energy-conserving, c) efficient and easy to implement, ideally a small modification to well-understood microfacet models. We present here a model based on the previously published ``back-vector'' formulation~\cite{BelcourBackvector} which meets these requirements. It is so simple a modification to a regular microfacet model, that we term it the ``Minimal Retroreflective Microfacet'' (MRM) model which achieves a plausible retro-reflective result.
